Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-22 paper.tex
Text wrapping
Add address for Carmichael1981
Add accessed date for XFOIL coeffs

\bibitem[Bachant and Wosnik(2015)]{Bachant2015-NACAXX20-XFOIL}
Bachant, P.; Wosnik, M.
\newblock NACA XX20 XFOIL Coefficients.
\newblock Zenodo. Available online: \url{http://dx.doi.org/10.5281/zenodo.32054} (accessed on \hl{Day Month} 2015).

\bibitem[Carmichael(1981)]{Carmichael1981}
Carmichael, B.H.
\newblock \emph{Low {R}eynolds Number Airfoil Survey Volume {I}}.
\newblock Technical Report, National Aeronautics and Space Administration: \hl{City, Country},
 1981.

>>>>

\bibitem[Bachant and Wosnik(2015)]{Bachant2015-NACAXX20-XFOIL} Bachant, P.;
Wosnik, M. \newblock NACA XX20 XFOIL Coefficients. \newblock Zenodo. Available
online: \url{http://dx.doi.org/10.5281/zenodo.32054} (accessed on 1 November
2015).

\bibitem[Carmichael(1981)]{Carmichael1981} Carmichael, B.H. \newblock \emph{Low
    {R}eynolds Number Airfoil Survey Volume {I}}. \newblock Technical Report,
National Aeronautics and Space Administration: Capistrano Beach, California,
USA, 1981.
